Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2017-12-03 PAPER.tex
compiled with Aaron's additions

\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
The middle 
two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
ensemble, $\langle\textbf{xe}^\dagger\rangle$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, the
inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}$ is multiplied into $\textbf{x}$,
the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}$), but
contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
of the off-diagonal terms in $\textbf{C}^{-1}$ while retaining the negative sign that arose from the inversion
of a diagonal-dominant matrix.
% XXX [ARP: we may want to write this all out explicitly in an appendix]

>>>>

\noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
The middle 
two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
ensemble, $\langle\textbf{xe}^\dagger\rangle$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, the
inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}_{r}$ is multiplied into $\textbf{x}$,
the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}_{r}$), but
contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
of the off-diagonal terms in $\textbf{C}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
of a diagonal-dominant matrix.
% XXX [ARP: we may want to write this all out explicitly in an appendix]
